\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-07 chapters/1_intro.tex
Steffen comments

\emph{Instance segmentation} is a task of computer vision consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
The most success in instance segmentation (IS) has been achieved by applying deep learning \cite{he2017mask,romera2016recurrent,liu2018affinity}. There are two main types of successful deep learning approaches to IS: proposal-based and proposal-free methods. Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances \cite{he2017mask,dai2016instance,li2017fully}. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut}. In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances comparable to proposal-based methods.

>>>>

\emph{Instance segmentation} is a computer vision task consisting in assigning each pixel of an image to an object instance. %, where the number of instances is usually not known in advance. 
Most recently, success in instance segmentation (IS) has been achieved by applying deep learning and there are two main types of successful deep learning approaches to IS: proposal-based \cite{he2017mask,dai2016instance,li2017fully} and proposal-free \cite{kong2018recurrent,novotny2018semi,kulikov2018instance,kirillov2017instancecut} methods. Proposal-based methods consist of two steps: detecting objects, for example by finding bounding boxes, and assigning pixels to the detected instances. Although these approaches have proven to be highly successful in instance segmentation competitions like MS COCO \cite{lin2014microsoft}, Pascal VOC2012 \cite{everingham2010pascal} and CityScapes \cite{cordts2016cityscapes}, they are not applicable to certain types of data, for example electron microscopy (EM) image volumes of neurons \cite{arganda2015crowdsourcing}, where objects are not approximated well by bounding boxes. 
% More motivation: They are at the same time limited by the quality of the object detection routine, which is hard to train on small datasets (but no ref for this)
Thus, there is a growing interest for more efficient proposal-free methods that perform IS by directly predicting pixel features and then grouping pixels into object instances. In this work, we focus on a common proposal-free method, where a Convolutional Neural Network (CNN) predicts affinities representing how likely it is for pairs of pixels to belong to the same instance. Recently, this approach was successfully applied both to neuron segmentation of 3D EM image stacks \cite{lee2017superhuman,wolf2018mutex} and instance segmentation of 2D urban scenes \cite{liu2018affinity}, where it achieved performances comparable to proposal-based methods.

### 2019-05-07 chapters/3_algorithm.tex
Steffen comments

We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that can describe in a simple form several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.

The proposed algorithm uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merging pairs of adjacent clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b} and \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).

>>>>

We now present a Generalized Algorithm for Signed Graphs Agglomerative Clustering (\algname) that describes several graph partitioning algorithms previously introduced in the literature and highlights the existence of new ones.

The proposed algorithm \ref{main_alg} uses a bottom-up approach starting with each node assigned to its own cluster and iteratively merges pairs of adjacent clusters. Intuitively, the algorithm starts by merging clusters with the strongest attractive interaction, corresponding to the highest positive weights in the graph, and it stops when the remaining clusters share only mutual repulsive interactions (see Fig. \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}b} and \hyperref[fig:intro_figure]{\ref*{fig:intro_figure}c}).
